### 2018-02-01 includes/appendix.tex
appendix

In this section, we discuss how we proved equisatisfiability
guarantees that transformations provide in \fuzzer{}. We assume that
the reader is familiar with SMT-LIB syntax. The transformations work
over boolean, integer, string literals and expressions, and regular
expressions.

@@

\subsection{Translate}
We now prove that \textit{Translate} transforms constraints into
equisatisfiable constraints. From above, we only need to show that for
every expression $e$, $\textit{Translate}(\eval (e)) = \eval
(\textit{Translate}(e))$. For now, we assume that \textit{Translate}
fixes the digits pointwise and we prove the stronger fact that
$\textit{Translate}$ also fixes characters pointwise in any string
expression. (I.e., $\textit{Translate}$ are bijections and further
that digits are not mapped to any other character.)

@@

The restriction that \textit{Translate} must fix the digit characters
can be relaxed if we are translating problem instances that do not use
\texttt{str.to.int} or \texttt{str.from.int}. Without these operators
we can show $\textit{Translate}(\eval (e)) = \eval
(\textit{Translate}(e))$ directly by induction without having to worry
about fixing digits pointwise.

>>>>

In this section, we informally discuss how we established
equisatisfiability guarantees that transformations provide in
\fuzzer{}. We assume that the reader is familiar with SMT-LIB
syntax. The transformations work over boolean, integer, string
literals and expressions, and regular expressions.

@@

\subsection{Translate}
We now prove that \textit{Translate} transforms constraints into
equisatisfiable constraints. From above, we only need to show that for
every expression $e$, the following is true: $\textit{Translate}(\eval
(e))$ = $\eval (\textit{Translate}(e))$. For now, we assume that
\textit{Translate} fixes the digits pointwise and we prove the
stronger fact that $\textit{Translate}$ also fixes characters
pointwise in any string expression. (I.e., $\textit{Translate}$ are
bijections and further that digits are not mapped to any other
character.)

@@

The restriction that \textit{Translate} must fix the digit characters
can be relaxed if we are translating problem instances that do not use
\texttt{str.to.int} or \texttt{str.from.int}. Without these operators
we can show $\textit{Translate}(\eval (e))$ = $\eval
(\textit{Translate}(e))$ directly by induction without having to worry
about fixing digits pointwise.
